 Casting multiple shadows: interactive data visualisation with tours and embeddings

### 2020-02-07 paper.Rmd
add citations

Choosing an appropriate embedding presents a challenge to the analyst. How does
an analyst know whether the embedding has captured the underlying topology and
geometry of the high dimensional space? The answer depends on the analyst's
workflow.  @Brehmer2014-hk characterised two main workflow steps that an
analyst performs when using embedding techniques: dimension reduction and
cluster orientation. The first relates to dimension reduction achieved by using
an embedding method, here an analyst wants to characterise and map meaning onto
the embedded form, for example identifying batch effects from a high throughput
sequencing experiment, or identifying a gradient or trajectory along the
embedded form. The second relates to using embeddings as part of a clustering
workflow. Here analysts are interested in identifying and naming clusters and
verifying them by either applying known labels or colouring by variables that
are a-priori known to distinguish clusters. Both of these workflow steps rely
on the embedding being 'faithful' or the original high dimensional dataset, and
become much more difficult when there is no underlying ground truth.

@@

my contribution + design of interface

>>>>

Choosing an appropriate embedding presents a challenge to the analyst. How does
an analyst know whether the embedding has captured the underlying topology and
geometry of the high dimensional space? The answer depends on the analyst's
workflow.  @Brehmer2014-hk characterised two main workflow steps that an
analyst performs when using embedding techniques: dimension reduction and
cluster orientation. The first relates to dimension reduction achieved by using
an embedding method, here an analyst wants to characterise and map meaning onto
the embedded form, for example identifying batch effects from a high throughput
sequencing experiment, or identifying a gradient or trajectory along the
embedded form @Nguyen2019-yh. The second relates to using embeddings as part of a clustering
workflow. Here analysts are interested in identifying and naming clusters and
verifying them by either applying known labels or colouring by variables that
are a-priori known to distinguish clusters. Both of these workflow steps rely
on the embedding being 'faithful' or the original high dimensional dataset, and
become much more difficult when there is no underlying ground truth.

@@
